Architectures for workflow integration in science gateways

### 2016-04-13 paper.tex
Minor updates

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage{subfig}
\usepackage{svg}
\usepackage{url}

\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}

@@

FLI-IAM, Labex PRIMES, Ludmer Centre

@@

\bibliographystyle{elsarticle-num} 
\bibliography{biblio}

>>>>

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage{subfig}
\usepackage{svg}
\usepackage{url}
\usepackage{flushend}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}

@@

\todo{FLI-IAM, Labex PRIMES, Ludmer Centre, whatever grant is funding
  POQ for integrating CBRAIN with PSOM.}

We warmly thank Rafael Ferreira da Silva for implementing the VIP
platform and creating Figure~\ref{fig:vip-architecture}.

@@

\todo{Review use of capitals in references}
\bibliographystyle{elsarticle-num} 
\bibliography{biblio}
